Msc Thesis Figures

### 2021-04-19 docs/msc_thesis_figures.Rmd
change titles

#### Networks
##### CHAP 1
```{r, message=FALSE, warning=FALSE, out.width="100%", fig.cap=""}
networks <- read_csv("../outputs/final/final_df_network_stats.csv") %>% 
  left_join(results_clean, by = c("scenario" = "scenarioId"))

>>>>

### Networks
##### CHAP 1
```{r, message=FALSE, warning=FALSE, out.width="100%", fig.cap=""}
networks <- read_csv("../outputs/final/final_df_network_stats.csv") %>% 
  left_join(results_clean, by = c("scenario" = "scenarioId"))
